Causal Roadmap

### 2023-01-16 docs/causal_roadmap.qmd
Set up targets. Better bibtex to auto-update bibliography from sub-collection for paper 3 from Zotero. Targets: one pipeline for each research question of causal roadmap, with data saved outside of git repo

---
title: "Causal Roadmap"
author: Lorenzo Fabbri
output:
  bookdown::pdf_document2:
    number_sections: false
  html_document: default
bibliography: references.bib
editor_options: 
  chunk_output_type: console
---

```{r}
#| label: setup
#| include: false
library(tidyverse)
```

```{r}
#| echo: false
# Type of adjustment set from DAG
type.mas <- "minimal"
# Type of effect to be estimated from DAG
type.effect <- "direct"
```

@@

```{r}
#| label: causal-graph
#| echo: false
#| fig.cap: Causal graph corresponding to structural equations.
#| fig.height: 3.0
#| fig.width: 3.0
causal.graph <- ggdag::dagify(A ~ W + U_A, Y ~ W + A + U_Y, W ~ U_W, 
                              exposure = "A", outcome = "Y") %>%
  ggdag::tidy_dagitty()
ggdag::ggdag(causal.graph) + ggdag::theme_dag()
```

@@

```{r}
#| echo: false
#| fig.cap: Simplified DAG for research question 1.
sdag1 <- ggdag::dagify(X_ti ~ W_t, 
                       Y ~ W_t + X_ti, 
                       exposure = "X_ti", outcome = "Y") %>%
  ggdag::tidy_dagitty() %>%
  ggdag::ggdag(text_size = 2, node_size = 10) + ggdag::theme_dag() +
  ggplot2::ggtitle("RQ1")
```

```{r}
#| echo: false
ggpubr::ggarrange(sdag1, ..., 
                  ncol = x, nrow = y)
```

@@

```{r}
#| echo: false
source("../DAGs/dag_v1.R")
source("../code/dags.R")

@@

```{r}
#| echo: false
#| fig.cap: DAG for Research question 1.
#| fig.height: 10.0
#| fig.width: 18.0
dag.rq1 <- dags$rq1 %>%
  dagitty::dagitty()
dag.rq1 %>% ggdag::tidy_dagitty() %>%
  ggdag::ggdag_status(text_size = 10, text_col = "black") +
  ggdag::theme_dag() + ggdag::scale_adjusted() +
  ggplot2::theme(legend.text = ggplot2::element_text(size = 20))
```

@@

```{r}
#| echo: false
dagitty::adjustmentSets(x = dag.rq1, 
                        type = type.mas, effect = type.effect)
```

>>>>

---
title: "Causal Roadmap"
keywords:
  - Causal Inference
  - Epidemiology
author:
  - name: "Lorenzo Fabbri"
    number: 1
    email: lorenzo.fabbri@isglobal.org
    orcid: 0000-0003-3031-322X
    attributes:
      corresponding: true
    affiliations:
      - ref: isg
      - ref: upf
affiliations:
  - id: isg
    name: ISGlobal
    city: Barcelona
    state: Spain
  - id: upf
    name: UPF
    city: Barcelona
    state: Spain
format:
  pdf:
    pdf-engine: pdflatex
    toc: false
bibliography: ../output/paper/bibliography.bib
link-citations: true
linkcolor: blue
header-includes:
  - \usepackage{setspace}\doublespacing
  - \usepackage[switch, pagewise, running]{lineno}
  - \linenumbers
  - \renewcommand\linenumberfont{\normalfont\small}
  - \usepackage{rotating}
  - \usepackage{float}
execute:
  echo: false
---

```{r}
#| label: setup
library(tidyverse)
```

```{r}
# Type of adjustment set from DAG
type.mas <- "minimal"
# Type of effect to be estimated from DAG
type.effect <- "direct"
```

@@

```{r}
#| label: causal-graph
#| fig.cap: Causal graph corresponding to structural equations.
#| fig.height: 3.0
#| fig.width: 3.0
causal.graph <- ggdag::dagify(A ~ W + U_A, Y ~ W + A + U_Y, W ~ U_W, 
                              exposure = "A", outcome = "Y") %>%
  ggdag::tidy_dagitty()
ggdag::ggdag(causal.graph) + ggdag::theme_dag()
```

@@

```{r}
#| fig.cap: Simplified DAG for research question 1.
sdag1 <- ggdag::dagify(X_ti ~ W_t, 
                       Y ~ W_t + X_ti, 
                       exposure = "X_ti", outcome = "Y") %>%
  ggdag::tidy_dagitty() %>%
  ggdag::ggdag(text_size = 2, node_size = 10) + ggdag::theme_dag() +
  ggplot2::ggtitle("RQ1")
```

```{r}
ggpubr::ggarrange(sdag1, 
                  ncol = 1, nrow = 1)
```

@@

```{r}
source("../DAGs/dag_v1.R")
source("../code/dags.R")

@@

```{r}
#| fig.cap: DAG for Research question 1.
#| fig.height: 10.0
#| fig.width: 18.0
dag.rq1 <- dags$rq1 %>%
  dagitty::dagitty()
dag.rq1 %>% ggdag::tidy_dagitty() %>%
  ggdag::ggdag_status(text_size = 10, text_col = "black") +
  ggdag::theme_dag() + ggdag::scale_adjusted() +
  ggplot2::theme(legend.text = ggplot2::element_text(size = 20))
```

@@

```{r}
dagitty::adjustmentSets(x = dag.rq1, 
                        type = type.mas, effect = type.effect)
```
